\plaintitle

### 2017-06-21 papers/IoT2017/analysis.tex
updates

\section{Discussion}
\label{sec:discussion}

@@

\subsection{Safety}
We now demonstrate that faulty or malicious prosumers cannot trade
excessive amounts of energy if normal prosumers follow the rules of
the trading workflow.  First, we can show that the net amount of
energy sold by prosumer $i$ for each timestep is at most
$\field{MAXEPA}_i$.  By definition, the amount of energy sold is less
than or equal to the amount of EPA obtained by prosumer $i$.

A prosumer can obtain EPA either by withdrawing from its smart meter
or by purchasing form another prosumer.  From its smart meter,
prosumer $i$ can withdraw at most $\field{MAXEPA}_i$.  Although the
prosumer may also buy EPA from another prosumer, this constitutes
buying energy, which decreases the net amount of energy sold with the
same amount.  Hence, the net amount of energy sold by prosumer $i$
cannot exceed $\field{MAXEPA}_i$.  By extending the argument, we can
show that the net amount of energy sold by a group of prosumers~$G$
cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, %we can
show that the net amount of energy bought by a group of prosumers $G$
cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.

>>>>

%!TEX root = paper.tex
\section{Discussion}
\label{sec:discussion}

@@

\subsection{Safety}
We now demonstrate that faulty or malicious prosumers cannot trade
excessive amounts of energy if normal prosumers follow the rules of
the trading workflow.  First, we can show that the net amount of
energy sold by prosumer $i$ for each timestep is at most
$\field{MAXEPA}_i$.  By definition, \textcolor{blue}{we assume that the smart meters enforce a constraint, which ensures that} the amount of energy sold is less
than or equal to the amount of EPA obtained by prosumer $i$.

A prosumer can obtain EPA either by withdrawing from its smart meter
or by purchasing form another prosumer.  From its smart meter,
prosumer $i$ can withdraw at most $\field{MAXEPA}_i$.  Although the
prosumer may also buy EPA from another prosumer, this constitutes
buying energy, which decreases the net amount of energy sold with the
same amount.  Hence, the net amount of energy sold by prosumer $i$
cannot exceed $\field{MAXEPA}_i$.  By extending the argument, we can
show that the net amount of energy sold by a group of prosumers~$G$
cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, %we can
%show that
 the net amount of energy bought by a group of prosumers $G$
cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.

### 2017-06-21 papers/IoT2017/concl.tex
updates

\Doug{Abhishek, as always, it would be best if we could revise this summary of the paper's contents to be a summary of lessons learned based upon our experiences to date!}
As the complexity of power systems increases due to the evolution of
power grids, decentralized transactive-energy IoT systems are emerging
to tackle this complexity. Ironically, these decentralized systems
also give rise to new privacy challenges, such as leakage of energy usage patterns, including the possibility of inference of future state of a prosumer, 
\Doug{Abhishek, please briefly list the key privacy challenges we cover in this paper.}
which are exacerbated by the stringent safety and
security requirements of power systems.

>>>>

\Doug{Abhishek, as always, it would be best if we could revise this summary of the paper's contents to be a summary of lessons learned based upon our experiences to date!}
As the complexity of power systems increases due to the evolution of
power grids, decentralized transactive-energy IoT systems are emerging
to tackle this complexity. Ironically, these decentralized systems
also give rise to new privacy challenges, \textcolor{blue}{such as leakage of energy usage patterns, including the possibility of inference of future state of a prosumer}, 
\Doug{Abhishek, please briefly list the key privacy challenges we cover in this paper.}
which are exacerbated by the stringent safety and
security requirements of power systems.

### 2017-06-21 papers/IoT2017/intro.tex
updates

Power grids are undergoing major changes due to rapid acceleration in
renewable energy resources, such as wind and solar power
\cite{5430489}.
% \cite{EIA2014}
For example, $4,\!143$ megawatts of solar panels were installed in the
third quarter of 2016 \cite{seia}. This capacity is estimated to grow
from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
battery technology costs per kWh have dropped significantly
\cite{stock2015powerful}, reaching grid parity.
% \cite{bronski2015economics}
The massive integration of renewable energy requires detailed
information and visibility into all aspects of the network, making it
hard to manage, especially in the presence of variable distributed
energy resources \cite{7452738}. A different vision for the future of
power-grid operations is therefore emerging: {\em a decentralized
  system in which local communities are arranged in microgrids}
\cite{rahimi2012transactive}. In this vision, energy generation,
transmission, distribution, and even storage (\emph{e.g.}, electric
vehicles in a community) can be strategically used to balance load and
demand spikes.

@@

% \Aron{Since SIGCHI does not have section numbers, this paragraph,
%  which describes the organization of the paper, is not very clear.}
The remainder of this paper is organized as follows: we first describe
the basic components of a transactive IoT microgrid and formulate
security, safety, and privacy requirements; we next introduce PETra
and describe the transactions and services used to implement it; we
then discuss how PETra satisfies the security, safety, and privacy
requirements; finally we compare our work on PETra with related work
and present concluding remarks.

>>>>

Power grids are undergoing major changes due to rapid acceleration in
renewable energy resources, such as wind and solar power
\cite{5430489}.
% \cite{EIA2014}
For example, $4,\!143$ megawatts of solar panels were installed in the
third quarter of 2016 \cite{seia}. This capacity is estimated to grow
from 4\% in 2015 to 29\% in 2040 \cite{Randal}. 
%At the same time,
%battery technology costs per kWh have dropped significantly
%\cite{stock2015powerful}, reaching grid parity.
% \cite{bronski2015economics}
The massive integration of renewable energy requires detailed
information and visibility into all aspects of the network, making it
hard to manage, especially in the presence of variable distributed
energy resources \cite{7452738}. A different vision for the future of
power-grid operations is therefore emerging: {\em a decentralized
  system in which local communities are arranged in microgrids}
\cite{rahimi2012transactive}. In this vision, energy generation,
transmission, distribution, and even storage (\emph{e.g.}, electric
vehicles in a community) can be strategically used to balance load and
demand spikes.

@@

% \Aron{Since SIGCHI does not have section numbers, this paragraph,
%  which describes the organization of the paper, is not very clear.}
%The remainder of
This paper is organized as follows: we first describe
the basic components of a transactive IoT microgrid and formulate
security, safety, and privacy requirements; we next introduce PETra
and describe the transactions and services used to implement it; we
then discuss how it satisfies the security, safety, and privacy
requirements; finally we 
%compare our work on PETra with 
describe related work
and present concluding remarks.

### 2017-06-21 papers/IoT2017/prelim.tex
update
updates

%!TEX root = paper.tex
\section{System Model and Requirements}

@@

A microgrid also typically contains a set of protection nodes that are
responsible for isolating faults on the feeder.  The
\emph{Distribution System Operator} (DSO) operations a set of
switching nodes to control the connection of the microgrid to the rest
of the distribution system. The DSO is responsible for regulating the
net electric power into and out of the microgrid. Starting from this
model, we next introduce the transactive microgrid model.

@@

Figure~\ref{fig:softwareArchitecture} shows the a decentralized
transactive microgrid with PETra.  In this figure, components marked
red are introduced to provide privacy in a safe and secure manner,
whereas components marked in blue are typical elements of a
decentralized transactive microgrid.
\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=0.7cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
\draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};

@@

\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]workflow for prosumers};
\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
\end{tikzpicture}
\caption{The Architecture of a Decentralized Transactive Microgrid with PETra.}
\label{fig:softwareArchitecture}
\end{figure}

>>>>

%!TEX root = paper.tex
%\vspace{-0.15in}
\section{System Model and Requirements}

@@

A microgrid also typically contains a set of protection nodes that are
responsible for isolating faults on the feeder.  The
\emph{Distribution System Operator} (DSO) operates %a set of
switching nodes to control the connection of the microgrid to the rest
of the distribution system. The DSO is responsible for regulating the
net electric power into and out of the microgrid. Starting from this
model, we next introduce the transactive microgrid model.

@@

Figure~\ref{fig:softwareArchitecture} shows a decentralized
transactive microgrid with PETra.  In this figure, components marked
red are introduced to provide privacy in a safe and secure manner,
whereas components marked in blue are typical elements of a
decentralized transactive microgrid.
\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=0.7cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
\draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};

@@

\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]workflow for prosumers};
\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
\end{tikzpicture}
\caption{Architecture of a Decentralized Transactive Microgrid with PETra.}
\label{fig:softwareArchitecture}
\end{figure}
